VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-28 snapshot_system/paper_intro.tex
update more on converged arch

Server virtualization is one of the most benefited area of adopting converged storage architecture.
Leading cloud platform providers such as Google AppEngine, Amazon AWS, 
Microsoft Azure and Alibaba have built such a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers.
Many VDI environment in private clouds are also adopting this converged architecture 
provided by Nutanix~\cite{NutanixPaper}, Simplivity and others. 
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines 
%as  instances of a guest operating system 
and their virtual disks are represented as virtual disk image files in the host operating system.
Frequent snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication

>>>>

Server virtualization is one of the most benefited area of adopting converged storage architecture.
Leading cloud platform providers such as Google AppEngine, Amazon AWS, 
Microsoft Azure and Alibaba have built such a converged compute and storage infrastructure and used
a distributed file system such as Google file system~\cite{googlefs03,hdfs10}
to glue a large number of commodity servers.
And such converged storage architecture also becomes increasingly popular 
in VDI environment in private clouds
provided by Nutanix~\cite{NutanixPaper}, Simplivity and others. 
% with local storage into a single cluster.
In such an environment,
%That  allows the use of scalable compute and storage, without incurring the costs and
%performance limitations associated with network storage.
each physical machine runs a number  of virtual machines 
%as  instances of a guest operating system 
and their virtual disks are represented as virtual disk image files in the host operating system.

As more and more production 
applications are running in virtualized environments in the cloud,
the need to protect these virtual machines against data loss is urgent.
Frequent snapshot backup of virtual disk images  can increase  the service reliability
and deduplication of redundant content blocks~\cite{venti02,bottleneck08}
 is necessary to substantially reduce the storage demand.
This is typically done through offloading backup workload from production 
server hosts and consolidating it on dedicated backup proxy servers (e.g. EMC Data Domain) or
backup services (e.g. Amazon S3). This approach simplifies the cluster architecture and 
avoids potential performance hits to the production applications when backup is in progress,
but it also brings its own problems:
From VM users' perspective, the cost of a dedicated backup storage is very high.
From cloud architecture's perspective, sending out pre-deduplication backup data wastes huge amount
of bandwidth. Finally and most importantly, such dedicated backup storage is either difficult to scale out
which would comprise the overall scalability of the converged architecture, 
or has to give up global deduplication in order to gain scalability which would then increase the backup cost.

Contrary to using dedicated backup storage for VM snapshots, 
in this paper we propose a collocated backup storage sitting on top of 
the existing distributed file system in a converged storage architecture,
and provide methodologies to address associated challenges: 
First, it must achieves good global deduplication 
while the computing resources are very limited and spread over every node. 
Second, it has to provide augmented fault isolation for the sharing of deduplicated data,
given that node failures in converged architecture are the norm rather than exception.
Finally, it needs to provide easily managable garbage collection so that user immediately
sees storage charge changes after he deletes a snapshot.

% low-cost VM-centric snapshot backup approach that is collocated within 
% the existing converged storage architecture. Our solution leverages the scalability of the underlying
% distributed file system and provides global data deduplication in a resource friendly manner.

%For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
%automatically conducts  the backup of virtual disk images to all active users every day.
%The cost of supporting a large number of concurrent backup streams is high
%because of the huge storage demand and the use of deduplication
